Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls

### 2019-12-11 Paper/paper-draft-Padgett-Thiam.Rmd
re-knit paper

```{r, echo = FALSE, include=FALSE}
library(knitr)
library(tidyverse)
library(gtrendsR)
library(dplyr)
library(ggplot2)
library(ggmap)
library(readxl)
library(shiny)
library(rtweet)
library(tidytext)
library(stringr)
library(lubridate)
library(quanteda)
library(SentimentAnalysis)
library(GGally)
library(repmis)
library(httr)
library(pander)
```

>>>>

```{r, echo = FALSE, include=FALSE}
library(knitr)
library(tidyverse)
library(gtrendsR)
library(dplyr)
library(ggplot2)
library(ggmap)
library(readxl)
library(shiny)
library(rtweet)
library(tidytext)
library(stringr)
library(lubridate)
library(quanteda)
library(SentimentAnalysis)
library(GGally)
library(repmis)
library(httr)
library(pander)
library(rsconnect)
```
